%%%%%%%%%%%% Document
\documentclass[letter]{resume}
\usepackage[letterpaper, left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}

\usepackage{color}            % allows usage of color fonts
\definecolor{blue1}{RGB}{31,97,242} % defines color and its name
\usepackage[colorlinks=true, allcolors=blue1, pdfborderstyle={/S/U/W 1}]{hyperref}

\usepackage{vwcol}
\usepackage{natbib}
\usepackage{cfr-lm}           % make old style numbers default
\usepackage{graphicx}

\usepackage{setspace}         %allows to change linespacing
\setstretch{1}                %linespacing
\clubpenalty=10000            % avoid clubs
\widowpenalty=10000           % avoid widows

\begin{document}

%%%%%%%%%%%% Title Section
\begin{center}
\name{José Roberto Torrens Hernández}
\contact {+52 55$\cdot$92$\cdot$00$\cdot$79$\cdot$51}
{\href{mailto://jtorren2@itam.mx}{jtorren2@itam.mx}}
{\href{https://www.linkedin.com/in/jrth}{in/JRTH}}

{\bf Finance student, Mexico City}

{\bf Summary}: {Undergraduate Finance student at Instituto Tecnológico Autónomo de México, ITAM.}

\emph{Interests}: {Private Equity, Corporate Finance, Venture Capital, Forensic Accounting.}
\end{center}

%%%%%%%%%%%% Education 
\section{Education} 
\begin{content}
{\bf Instituto Tecnológico Autónomo de México} \emph {} \hfill {\bf 2017 -- 2023} \\ 
{B.Sc. ITAM, \emph{Finance}} \hfill \emph {Mexico City}

\emph{Availability}: {Full time as of january 2024.}

\sectionlineskip
\end{content}

%%%%%%%%%%%% Experience
\section{Experience}
\begin{content}

\begin{position}{e-Commerce Retailer}{2018 – Present}{}{}{}
  \item Successfully built and managed an online store, achieved {\emph{Top-Rated Seller}} status within first 8 months.
  \item Monthly sales of {\em\$}1K USD and 99 per cent positive feedback rating since 2019.
  \item Communicated with customers to answer questions {\em\&} provide further details about items for sale. 
  \item Compiled all the accounting information, accounts receivable, accounts payable.
  \item Preparation of annual financial statements and related financial statements.
  \item Research of current applicable sales trends.
  \item Managed foreign and domestic payments.
  \item Excellent written and verbal communication.
  
\end{position}
\vspace{-.0001 \baselineskip}

\begin{position}{Inside Sales Representative}{2015 – 2018}{}{}{}
  \item Presented, promoted, and sold products and services using solid arguments to existing and prospective customers.
  \item Prospect and qualify new sales leads.
  \item Schedule meetings and presentations with prospects.
  \item Maintain a well-developed pipeline of prospects.
  \item Develop strong, ongoing relationships with prospects and customers.
  \item Reached out to customer leads through cold calling and email marketing.
\end{position}
\vspace{-.5\baselineskip}

\sectionlineskip
\end{content}

%%%%%%%%%%%%  Projects
%%%%%%%%%%%% \section{Projects \textbf{\em\&} Extracurriculars} 
%%%%%%%%%%%% \begin{content}
%%%%%%%%%%%% \begin{position}{La Gaceta de Ciencia Política}{Feb 2022 -- present}{\normalfont\href{https://gacetadecpol.com/}{\texttt{gacetadecpol.com}}}{\emph{Editorial Board}}{}
%%%%%%%%%%%% {\emph{Practice areas}}: Research, Academic Writing, and Editorial Design.
%%%%%%%%%%%% \end{position}

%%%%%%%%%%%% \begin{position}{Model United Nations}{2013 -- 2017}{\normalfont\href{https://www.linkedin.com/in/jtorrensh/}{\texttt{in/jtorrensh}}}{\emph{Delegate, Chairman, Moderator, Director, Staff, etc.}}{}
%%%%%%%%%%%% \item With more than 5 years of experience in international and national student conferences as an organizer and participant, being my most important experience the \emph{United Nations Model of the H. Congreso de la Unión}, Congresmun.
%%%%%%%%%%%% \end{position}
%%%%%%%%%%%% \sectionlineskip
%%%%%%%%%%%% \end{content}

%%%%%%%%%%%%  Courses
\section{Courses \textbf{\em\&} Certifications} 
\begin{content}
{\bf Coursera} \enspace {\href{https://drive.google.com/file/d/1DdNk74VG2TBfZJ3zGDNORk9Kxl3llNmX/view}{\texttt{jtorrens.courses/Excel}} 
{\em Excel Skills for Business: Essentials}}
\hfill {\bf Feb 2020}

{\bf Bloomberg LP} \enspace {\href{https://drive.google.com/file/d/17CiJctohYOMf9Ysp29AbRw_wlObl3amE/view}{\texttt{jtorrens.courses/Bloomberg}} 
{\em Bloomberg Market Concepts}}
\hfill {\bf Dec 2019}  \\
\emph{Practice areas}: Bloomberg Terminal, Economic Indicators, Currencies, Fixed Income, Equities.

{\bf Hanban (HSK 2)} \enspace {\href{https://drive.google.com/file/d/1BuRuxpN5NopmcDIbGKOu1IZeScyjribz/view}{\texttt{jtorrens.courses/Hanban}}
{\em Hanyu Shuiping Kaoshi}}
\hfill {\bf Oct 2015}
\sectionlineskip
\end{content}

%%%%%%%%%%%% Technical Skills
\section{Technical Skills}
\begin{content}
\begin{tabular}{ @{} >{\bf}l @{\hspace{6ex}} l }
  Programming Languages & Python (novice).\\ 
  Tools \textbf{\em\&} Technologies & MS Office (advanced), SAP (novice).\\
  Languages & Spanish (native), English (fluent), Chinese (HSK 2).
\end{tabular}

%%%%%%%%%%%%  COURSE WORK
\section{Skills}
  \centering
\begin{tabular}{ c c c }
{\bf Finance} & {\bf Data analysis} & {\bf Soft Skills} \\
[1 \smallskipamount]
Accounting & Data processing &  Problem-solving\\ 
Financial management & Data analysis  & Critical thinking \\
Financial planning & Data structures & Risk analysis \\
Economics &  Data management & Strategic planning \\
Invoicing {\em\&} Billing  & Data visualizations & Logical thinking
\end{tabular}

\sectionlineskip
\end{content}

\end{document}